---
title: "Problem Set 11"
author: "David Rügamer, Julia Terhart, Philipp Kopper"
date: "29 June 2020"
output:
 pdf_document: default
 html_document: default
---

# Resources

1) Accept the invitation to the assignment of this problem set:
https://classroom.github.com/a/G2LqHW4E

# Application

We simulate some data now.
We want to work with stock market data -- we simulate three different stock prices for each single day in 2019.
All follow a normal distribution and are somewhat correlated.

```{r}
set.seed(06072020)
stock_data <- data.frame(
  time = as.Date("2019-01-01") + 0:364,
  x = rnorm(365, 15, 2)
)
stock_data$y = rnorm(365, 0.25 * stock_data$x + 15, 3)
stock_data$z = rnorm(365, 0.3 * stock_data$x + 20, 4)
```

a) Create a new `data.frame` which collapses the data so that it looks like the following (or similar).
(Of course all the information of `stock_data` should also be in the new `data.frame`).
Make use of the `tidyr` package.

```{r}
data.frame(
  time = rep("2019-01-01", 3),
  stock = c("x", "y", "z"),
  price = c(stock_data$x[1:3])
)
```

b) Try to produce the same data set using the `reshape2` package.

c) According to Hadley Wickham (the author of R4DS) why is your new data set tidy?

1. Each variable forms a column.
2. Each observation forms a row.
3. Each type of observational unit forms a table.

d) Find the function from the `tidyr` package that reverts the previously constructed tidy data to `stock_data`.

e) Use the `dplyr` package to group the data by week and compute their mean.
Use `ggplot2` to plot the weekly stock prices __nicely__.

# Transfer

[`OpenML`](https://www.openml.org/) is an inclusive movement to build an open, organized, online ecosystem for machine learning. 
They facilitate a great environment for open machine learning.
For machine learning, one typically needs data.
For now, we use `OpenML` as a data warehouse.
At later points in your study, you might come back here for a different purpose.

a) Get the data set we want to work with from `OpenML`: 
https://www.openml.org/d/41021

Read the data description (in fact, the data is very interesting).
Download it as `.csv` and load it into `R`.
Store the data in your repository and make sure that using your code we can replicate your results.
(In fact, this is very important: In the Take-home exam we also expect this from you and if this does not work you will score 0 on the problem.)

b) The data is messy.
Some types are not correct (e.g. character instead of numeric, no factors).
Correct the types.
Hint: For some columns like `Year` you could use both, factors or numerics.

c) There is missing data in the data set.
Use the `dplyr` package to fill all the missing values with the mean of the respective column.
For which columns may this be problematic?


\pagebreak

```{r}
sessionInfo()
```

You can hand in this problem set by the 6th of July to receive feedback.